\documentclass{article}

\usepackage{hyperref}
\usepackage{graphicx}

\author{Nick Werle}
\title{P7 Submission}

\begin{document}
\maketitle
\section{Preamble}
This report's source files will be made available at \url{https://github.com/NickWer/CEG3900_P7}

\section{Task 1}
The user interface is okay. It seems really odd that it forced me to provide a username and password. Perhaps this is so users can track their contributions? Anyways other than that it seemed fine - nothing special.
My biggest critique of this app is probably just that - nothing special.
It's strange because there's no easy way to see just what work my phone did while charging, which makes me wonder what the traditional motivation is, outside of just a general sense of goodwill for furthering science.
In fact, opening the app does so little good that it actually has a bar at the bottom instructing you to just close the app and lock your phone - what good does that do me?

Anways, overall my impression of the app is that it's cool. It's cool at a technical level, in that it distributes workloads and solves tough problems.
On the other hand as a user, I can't really imagine wanting to install it - my experience as a user is that I just ignore it and each morning when I wake up my phone phone feels about as hot as molten lava.

If I could change something, I think it would be to provide some what to see what good my phone's effort actually has provided - just what, if anything, it was able to find/calculate.

\section{Task 2}
\end{document}
